---
title: "Prompt Accuracy Report"
format:
  html:
    toc: true
    code-fold: true
    embed-resources: true
editor: source
params:
  prompt_file: "prompts/prompt.md"
  model_filter: "claude-sonnet-4-20250514"
---

```{r setup, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
options(stringsAsFactors = FALSE, digits = 3)
library(tidyverse)
library(knitr)
library(DBI)
library(RPostgres)
```

```{r data}
prompt_file  <- params$prompt_file
model_filter <- params$model_filter
veggies <- c("ramp", "card_advantage", "targeted_disruption", "mass_disruption")

# --- Pull Claude results from PostgreSQL ---
con <- DBI::dbConnect(
  RPostgres::Postgres(),
  host     = Sys.getenv("DB_HOST"),
  port     = as.integer(Sys.getenv("DB_PORT")),
  user     = Sys.getenv("DB_USER"),
  password = Sys.getenv("DB_PASSWORD"),
  dbname   = "mtgcards"
)

df_claude <- DBI::dbGetQuery(con, "
  SELECT
    card_name,
    key   AS mechanic,
    value AS claude_tier
  FROM public.labeled,
  jsonb_each_text(raw_json - 'card_name')
  WHERE prompt_file = $1
    AND model = $2
", params = list(prompt_file, model_filter)) |>
  tibble::as_tibble() |>
  filter(mechanic %in% veggies)

DBI::dbDisconnect(con)

# --- Load KF ground-truth labels ---
df_kf_raw <- read_csv("tags-labeled - KF.csv")

df_kf <- df_kf_raw |>
  mutate(KF_tags = map(KF, ~ str_trim(unlist(str_split(.x, ";"))))) |>
  select(name, KF_tags) |>
  unnest(KF_tags) |>
  filter(KF_tags != "", !is.na(KF_tags)) |>
  separate(KF_tags, into = c("kf_tag", "kf_tier"), sep = ": ", extra = "merge") |>
  filter(kf_tag %in% veggies)

# Cards tagged by BOTH KF and Claude (for at least one veggie mechanic)
both_tagged_cards <- intersect(
  unique(df_kf$name),
  unique(df_claude$card_name)
)

# --- Join (restricted to cards both sides tagged) ---
# Full join so we capture:
#   - KF tagged, Claude tagged   (both tiers present)
#   - KF tagged, Claude missed   (claude_tier NA)
#   - KF did NOT tag, Claude tagged (kf_tier NA) — false positives
df_compare <- full_join(
  df_kf  |> filter(name %in% both_tagged_cards),
  df_claude |> filter(card_name %in% both_tagged_cards),
  by = c("name" = "card_name", "kf_tag" = "mechanic")
)

# Rows where KF had an opinion
df_kf_has_tag    <- df_compare |> filter(!is.na(kf_tag))
# False positives: Claude tagged, KF did not
df_false_pos     <- df_compare |> filter(is.na(kf_tag), !is.na(claude_tier))
```

## Overview

Prompt: `r prompt_file` | Model: `r model_filter`

```{r overview}
tibble(
  metric = c(
    "Cards tagged by both KF and Claude",
    "KF mechanic tags (veggies, shared cards)",
    "Claude mechanic tags (veggies, shared cards)"
  ),
  value = c(
    length(both_tagged_cards),
    nrow(df_kf   |> filter(name %in% both_tagged_cards)),
    nrow(df_claude |> filter(card_name %in% both_tagged_cards))
  )
) |> kable()
```

## Mechanic Detection Accuracy

For each of the four core mechanics, did Claude tag the cards KF tagged?  Overall accuracy `r mean(is.na(df_kf_has_tag$kf_tier) == is.na(df_kf_has_tag$claude_tier)) |> round(3)`

*Recall* = fraction of KF-tagged card/mechanic pairs that Claude also tagged.
*Precision* = fraction of Claude-tagged pairs that KF also tagged (among reviewed cards).

```{r detection}
recall_tbl <- df_kf_has_tag |>
  group_by(mechanic = kf_tag) |>
  summarise(
    kf_tags      = n(),
    claude_tagged = sum(!is.na(claude_tier)),
    accuracy = mean(is.na(kf_tier) == is.na(claude_tier)), 
    recall       = mean(!is.na(claude_tier)),
    .groups = "drop"
  )

precision_tbl <- df_compare |>
  filter(!is.na(claude_tier)) |>
  group_by(mechanic = kf_tag) |>
  summarise(
    claude_tags    = n(),
    kf_confirmed   = sum(!is.na(kf_tier)),
    precision      = mean(!is.na(kf_tier)),
    .groups = "drop"
  ) |>
  filter(!is.na(mechanic))

left_join(recall_tbl, precision_tbl, by = "mechanic") |>
  arrange(desc(kf_tags)) |>
  kable()
```

## Mislabeled Categories

Cards where Claude and KF disagree on whether a mechanic applies at all.

```{r mislabeled}
# False negatives: KF tagged the mechanic, Claude didn't
df_fn <- df_kf_has_tag |>
  filter(is.na(claude_tier)) |>
  transmute(card = name, mechanic = kf_tag, kf = kf_tier, claude = "(not tagged)")

# False positives: Claude tagged the mechanic, KF didn't
df_fp <- df_claude |>
  filter(card_name %in% both_tagged_cards) |>
  anti_join(df_kf, by = c("card_name" = "name", "mechanic" = "kf_tag")) |>
  transmute(card = card_name, mechanic, kf = "(not tagged)", claude = claude_tier)

bind_rows(df_fn, df_fp) |>
  arrange(card, mechanic) |>
  kable()
```

## Tier Accuracy

Among cards where both KF and Claude agreed the mechanic applies, how often did they assign the same tier?

Overall tier accuracy (veggies): `r mean(df_kf_has_tag$kf_tier == df_kf_has_tag$claude_tier, na.rm = TRUE) |> round(3)`

```{r tier-accuracy}
df_kf_has_tag |>
  filter(!is.na(kf_tier), !is.na(claude_tier)) |>
  group_by(mechanic = kf_tag) |>
  summarise(
    n            = n(),
    tier_accuracy = mean(kf_tier == claude_tier),
    .groups = "drop"
  ) |>
  arrange(desc(n)) |>
  kable()
```

## Tier Confusion

Where Claude and KF both tagged a mechanic but assigned different tiers, what did each assign?

```{r tier-confusion}
df_kf_has_tag |>
  filter(!is.na(kf_tier), !is.na(claude_tier), kf_tier != claude_tier) |>
  count(mechanic = kf_tag, kf_tier, claude_tier) |>
  arrange(mechanic, desc(n)) |>
  kable()
```

## False Negatives

Cards KF tagged that Claude missed (by mechanic).

```{r false-negatives}
df_kf_has_tag |>
  filter(is.na(claude_tier)) |>
  select(card = name, mechanic = kf_tag, kf_tier) |>
  arrange(mechanic, card) |>
  kable()
```

## False Positives

Cards Claude tagged that KF did not (among reviewed cards).

```{r false-positives}
df_compare |>
  filter(!is.na(claude_tier), is.na(kf_tag)) |>
  select(card = name, mechanic = kf_tag, claude_tier) |>
  arrange(claude_tier, card) |>
  kable()
```
