---
title: "Prompt Accuracy Report"
format:
  html:
    toc: true
    code-fold: true
    embed-resources: true
editor: source
params:
  prompt_file: "prompts/prompt4.md"
  model_filter: "claude-opus-4-8"
---

```{r setup, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
options(stringsAsFactors = FALSE, digits = 3)
library(tidyverse)
library(jsonlite)
library(DBI)
library(knitr)

query_postgres <- function(query, ...) {
  
  # --- Pull Claude results from PostgreSQL ---
  con <- DBI::dbConnect(
    RPostgres::Postgres(),
    host     = Sys.getenv("DB_HOST"),
    port     = as.integer(Sys.getenv("DB_PORT")),
    user     = Sys.getenv("DB_USER"),
    password = Sys.getenv("DB_PASSWORD"),
    dbname   = "mtgcards"
  )
  
  df <- DBI::dbGetQuery(con, query, ...)
  
  DBI::dbDisconnect(con)
  tibble::tibble(df)
}
```

```{r data}
prompt_file  <- params$prompt_file
model_filter <- params$model_filter
veggies <- c("ramp", "card_advantage", "targeted_disruption", "mass_disruption")

# --- Pull Claude results from PostgreSQL ---
df_claude <- query_postgres("
select card_name, raw_json
from public.labeled
where prompt_file = $1
  and model = $2
", params = list(prompt_file, model_filter)) 
df_claude_tags <- df_claude %>% 
  mutate(raw_json = map(as.character(raw_json), fromJSON)) %>%
  unnest_longer(raw_json, indices_to = "category", values_to = "tier") %>%
  filter(!category %in% c("card_name", "low_confidence")) %>%
  select(card_name, category, tier)

# --- Load KF ground-truth labels ---
df_kf <- query_postgres("
select card_name, kf
from public.labeled_kf_final
")
df_kf_tags <- df_kf %>% 
  mutate(kf = map(as.character(kf), fromJSON)) %>%
  unnest_longer(kf, indices_to = "category", values_to = "tier")

# dataset with rankings of both
df_cards <- df_claude %>% inner_join(df_kf, by = c("card_name"))
df_tags <- df_claude_tags %>% 
  full_join(df_kf_tags, by = c("card_name", "category"), suffix = c("_claude", "_kf")) %>% 
  filter(card_name %in% df_cards$card_name)
df_tags_veggies <- df_tags |> filter(category %in% veggies)

# list of valid mechanics
df_mechanics <- df_tags |> count(category, sort = T)
```

## Overview

Prompt: `r prompt_file` | Model: `r model_filter`.

For each of the categories, did Claude tag the cards KF tagged?  Overall accuracy `r mean(is.na(df_tags$tier_kf) == is.na(df_tags$tier_claude)) |> round(3)`.  Veggies only accuracy `r mean(is.na(df_tags_veggies$tier_kf) == is.na(df_tags_veggies$tier_claude)) |> round(3)`.

Among cards where both KF and Claude agreed the mechanic applies, how often did they assign the same tier?  Overall accuracy `r mean(df_tags$tier_kf == df_tags$tier_claude, na.rm = T) |> round(3)`.  Veggies only accuracy `r mean(df_tags_veggies$tier_kf == df_tags_veggies$tier_claude, na.rm = T) |> round(3)`.

```{r overview}
tibble(
  metric = c(
    "Cards tagged by both KF and Claude",
    "KF mechanic tags (all categories, shared cards)",
    "Claude mechanic tags (all categories, shared cards)",
    "KF mechanic tags (veggies, shared cards)",
    "Claude mechanic tags (veggies, shared cards)"
  ),
  value = c(
    nrow(df_cards),
    nrow(df_tags   |> filter(!is.na(tier_kf))),
    nrow(df_tags |> filter(!is.na(tier_claude))),
    nrow(df_tags_veggies   |> filter(!is.na(tier_kf))),
    nrow(df_tags_veggies |> filter(!is.na(tier_claude)))
  )
) |> kable()
```

## Mechanic Detection Accuracy

For each of the categories, did Claude tag the cards KF tagged?  Overall accuracy `r mean(is.na(df_tags$tier_kf) == is.na(df_tags$tier_claude)) |> round(3)`.  Veggies only accuracy `r mean(is.na(df_tags_veggies$tier_kf) == is.na(df_tags_veggies$tier_claude)) |> round(3)`.

```{r detection}
df_tags %>% 
  group_by(category) %>% 
  summarise(
    n = n(), 
    n_kf = sum(!is.na(tier_kf)), 
    n_claude = sum(!is.na(tier_claude)), 
    accuracy = mean(!is.na(tier_kf) == !is.na(tier_claude))
  ) %>% 
  arrange(desc(n)) |>
  kable()
```

## Tier Accuracy

Among cards where both KF and Claude agreed the mechanic applies, how often did they assign the same tier?  Overall accuracy `r mean(df_tags$tier_kf == df_tags$tier_claude, na.rm = T) |> round(3)`.  Veggies only accuracy `r mean(df_tags_veggies$tier_kf == df_tags_veggies$tier_claude, na.rm = T) |> round(3)`.

```{r tier-accuracy}
df_tags %>% 
  filter(!is.na(tier_kf), !is.na(tier_claude)) |>
  group_by(category) %>% 
  summarise(
    n = n(), 
    tier_accuracy = mean(tier_kf == tier_claude),
  ) %>% 
  arrange(desc(n)) |>
  kable()
```

## False Negatives

Cards KF tagged that Claude missed, grouped by mechanic.

::: {.panel-tabset}

```{r false-negatives, results='asis'}
df_fn <- df_tags |>
  filter(is.na(tier_claude), !is.na(tier_kf)) %>%
  arrange(card_name)

for (mech in df_mechanics$category) {
  cat(paste0("\n### ", mech, "\n\n"))
  sub_df <- df_fn |> filter(category == mech) |> select(card_name, tier_kf)
  if (nrow(sub_df) > 0) {
    print(kable(sub_df, row.names = FALSE))
  } else {
    cat("*None*\n\n")
  }
}
```

:::

## False Positives

Cards Claude tagged that KF did not, grouped by mechanic.

::: {.panel-tabset}

```{r false-positives, results='asis'}
df_fp <- df_tags |>
  filter(!is.na(tier_claude), is.na(tier_kf)) %>%
  arrange(card_name)

for (mech in df_mechanics$category) {
  cat(paste0("\n### ", mech, "\n\n"))
  sub_df <- df_fp |> filter(category == mech) |> select(card_name, tier_claude)
  if (nrow(sub_df) > 0) {
    print(kable(sub_df, row.names = FALSE))
  } else {
    cat("*None*\n\n")
  }
}
```

:::


