---
title: "Two-Pass Accuracy Report"
format:
  html:
    toc: true
    code-fold: true
    embed-resources: true
editor: source
params:
  prompt_file: "prompts/prompt10.md"
  feedback_prompt_file: "prompts/feedback_prompt.md"
  model_filter: "claude-opus-4-8"
---

```{r setup, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
options(stringsAsFactors = FALSE, digits = 3)
library(tidyverse)
library(jsonlite)
library(DBI)
library(knitr)

query_postgres <- function(query, ...) {
  con <- DBI::dbConnect(
    RPostgres::Postgres(),
    host     = Sys.getenv("DB_HOST"),
    port     = as.integer(Sys.getenv("DB_PORT")),
    user     = Sys.getenv("DB_USER"),
    password = Sys.getenv("DB_PASSWORD"),
    dbname   = "mtgcards"
  )
  df <- DBI::dbGetQuery(con, query, ...)
  DBI::dbDisconnect(con)
  tibble::tibble(df)
}
```

```{r data}
prompt_file          <- params$prompt_file
feedback_prompt_file <- params$feedback_prompt_file
model_filter         <- params$model_filter
veggies <- c("ramp", "card_advantage", "targeted_disruption", "mass_disruption")

# --- Pull two-pass results ---
df_raw <- query_postgres("
  select card_name, raw_json_pass1, raw_json_final
  from public.labeled_two_pass
  where prompt_file = $1
    and feedback_prompt_file = $2
    and model = $3
", params = list(prompt_file, feedback_prompt_file, model_filter))

parse_tags <- function(df, json_col, pass_label) {
  df %>%
    select(card_name, raw_json = !!sym(json_col)) %>%
    filter(!is.na(raw_json)) %>%
    mutate(raw_json = map(as.character(raw_json), fromJSON)) %>%
    unnest_longer(raw_json, indices_to = "category", values_to = "tier") %>%
    filter(category != "card_name") %>%
    select(card_name, category, tier) %>%
    rename(!!paste0("tier_", pass_label) := tier)
}

df_pass1 <- parse_tags(df_raw, "raw_json_pass1", "pass1")
df_final <- parse_tags(df_raw, "raw_json_final", "final")

# --- Load KF ground-truth ---
df_kf <- query_postgres("select card_name, kf from public.labeled_kf_final")
df_kf_tags <- df_kf %>%
  mutate(kf = map(as.character(kf), fromJSON)) %>%
  unnest_longer(kf, indices_to = "category", values_to = "tier_kf")

shared_cards <- intersect(df_raw$card_name, df_kf$card_name)

# Three-way full join: one row per (card, category) pair seen by ANY source.
# This correctly penalises false positives (Claude-only tags) alongside false negatives.
all_pairs <- bind_rows(
  df_kf_tags %>% filter(card_name %in% shared_cards) %>% select(card_name, category),
  df_pass1   %>% filter(card_name %in% shared_cards) %>% select(card_name, category),
  df_final   %>% filter(card_name %in% shared_cards) %>% select(card_name, category)
) %>% distinct()

df_tags <- all_pairs %>%
  left_join(df_kf_tags %>% filter(card_name %in% shared_cards), by = c("card_name", "category")) %>%
  left_join(df_pass1   %>% filter(card_name %in% shared_cards), by = c("card_name", "category")) %>%
  left_join(df_final   %>% filter(card_name %in% shared_cards), by = c("card_name", "category"))

df_tags_veggies <- df_tags %>% filter(category %in% veggies)

df_mechanics <- df_tags %>% count(category, sort = TRUE)
```

## Overview

Prompt: `r prompt_file` | Feedback: `r feedback_prompt_file` | Model: `r model_filter`

Cards compared against KF ground truth: **`r length(shared_cards)`**

**Mechanic detection accuracy** (did Claude tag the same mechanics as KF?):

```{r overview-detection}
tibble(
  pass = c("Pass 1", "Final (Pass 2)"),
  overall = c(
    mean(is.na(df_tags$tier_kf) == is.na(df_tags$tier_pass1)),
    mean(is.na(df_tags$tier_kf) == is.na(df_tags$tier_final))
  ),
  veggies_only = c(
    mean(is.na(df_tags_veggies$tier_kf) == is.na(df_tags_veggies$tier_pass1)),
    mean(is.na(df_tags_veggies$tier_kf) == is.na(df_tags_veggies$tier_final))
  )
) %>% kable(digits = 3)
```

**Tier accuracy** (among cards both KF and Claude tagged, how often did tiers agree?):

```{r overview-tier}
tibble(
  pass = c("Pass 1", "Final (Pass 2)"),
  overall = c(
    mean(df_tags$tier_kf == df_tags$tier_pass1, na.rm = TRUE),
    mean(df_tags$tier_kf == df_tags$tier_final, na.rm = TRUE)
  ),
  veggies_only = c(
    mean(df_tags_veggies$tier_kf == df_tags_veggies$tier_pass1, na.rm = TRUE),
    mean(df_tags_veggies$tier_kf == df_tags_veggies$tier_final, na.rm = TRUE)
  )
) %>% kable(digits = 3)
```

## Changes Made by Pass 2

```{r changes}
df_changed <- df_tags %>%
  filter(!is.na(tier_pass1) | !is.na(tier_final)) %>%
  filter(
    coalesce(tier_pass1, "__NA__") != coalesce(tier_final, "__NA__")
  ) %>%
  select(card_name, category, tier_kf, tier_pass1, tier_final) %>%
  arrange(category, card_name)

cat(paste0("Pass 2 changed ", nrow(df_changed), " mechanic ratings across ", n_distinct(df_changed$card_name), " cards.\n"))

df_changed %>% kable()
```

## Mechanic Detection Accuracy by Category

```{r detection-by-category}
df_tags %>%
  group_by(category) %>%
  summarise(
    n_kf        = sum(!is.na(tier_kf)),
    n_pass1     = sum(!is.na(tier_pass1)),
    n_final     = sum(!is.na(tier_final)),
    acc_pass1   = mean(!is.na(tier_kf) == !is.na(tier_pass1)),
    acc_final   = mean(!is.na(tier_kf) == !is.na(tier_final))
  ) %>%
  arrange(desc(n_kf)) %>%
  kable(digits = 3)
```

## Tier Accuracy by Category

```{r tier-by-category}
df_tags %>%
  filter(!is.na(tier_kf)) %>%
  group_by(category) %>%
  summarise(
    n           = n(),
    tier_acc_pass1 = mean(tier_kf == tier_pass1, na.rm = TRUE),
    tier_acc_final = mean(tier_kf == tier_final, na.rm = TRUE)
  ) %>%
  arrange(desc(n)) %>%
  kable(digits = 3)
```

## False Negatives — Pass 1 vs Final

Cards KF tagged that each pass missed, grouped by mechanic.

::: {.panel-tabset}

```{r false-negatives, results='asis'}
df_fn_p1    <- df_tags %>% filter( is.na(tier_pass1), !is.na(tier_kf))
df_fn_final <- df_tags %>% filter( is.na(tier_final), !is.na(tier_kf))

for (mech in df_mechanics$category) {
  cat(paste0("\n### ", mech, "\n\n"))
  p1_sub    <- df_fn_p1    %>% filter(category == mech) %>% select(card_name, tier_kf) %>% rename(tier_kf_pass1 = tier_kf)
  final_sub <- df_fn_final %>% filter(category == mech) %>% select(card_name, tier_kf) %>% rename(tier_kf_final = tier_kf)
  combined  <- full_join(p1_sub, final_sub, by = "card_name") %>% arrange(card_name)
  if (nrow(combined) > 0) {
    print(kable(combined, row.names = FALSE))
  } else {
    cat("*None*\n\n")
  }
}
```

:::

## False Positives — Pass 1 vs Final

Cards each pass tagged that KF did not, grouped by mechanic.

::: {.panel-tabset}

```{r false-positives, results='asis'}
df_fp_p1    <- df_tags %>% filter(!is.na(tier_pass1), is.na(tier_kf))
df_fp_final <- df_tags %>% filter(!is.na(tier_final), is.na(tier_kf))

for (mech in df_mechanics$category) {
  cat(paste0("\n### ", mech, "\n\n"))
  p1_sub    <- df_fp_p1    %>% filter(category == mech) %>% select(card_name, tier_pass1)
  final_sub <- df_fp_final %>% filter(category == mech) %>% select(card_name, tier_final)
  combined  <- full_join(p1_sub, final_sub, by = "card_name") %>% arrange(card_name)
  if (nrow(combined) > 0) {
    print(kable(combined, row.names = FALSE))
  } else {
    cat("*None*\n\n")
  }
}
```

:::
