---
title: "Tagging Results"
format: 
  html:
    toc: true
    code-fold: true
editor: source
---

```{r setup, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
options(stringsAsFactors = F, digits = 3)
library(tidyverse)
library(knitr)
library(jsonlite)
```


```{r data}
claude_tags <- fromJSON("tags-sonnet-46.json")
df_claude <- tibble(
    name = names(claude_tags),
    data = claude_tags
) %>%
  unnest_longer(data) %>% 
  rename(claude_tag = data_id, claude_tier = data)

df <- read_csv("tags-labeled - KF.csv")
df_split <- df %>% 
  mutate(
    tags = map(collapsed, ~ unlist(str_split(.x, ";"))), 
    KF_tags = map(KF, ~ unlist(str_split(.x, ";"))), 
    tags = map(tags, str_trim), 
    KF_tags = map(KF_tags, str_trim)
    )
# df_claude <- df_split %>%
#   select(name, tags) %>%
#   unnest(tags) %>% 
#   separate(tags, c("claude_tag", "claude_tier"), ": ")
df_kf <- df_split %>%
  select(name, KF_tags) %>%
  unnest(KF_tags)%>% 
  filter(KF_tags != "") %>% 
  separate(KF_tags, c("kf_tag", "kf_tier"), ": ")

df_compare <- full_join(
  df_kf, 
  df_claude, 
  by = c("name", "kf_tag" = "claude_tag")
) %>% 
  filter(!is.na(kf_tag))
df_compare_veggies <- df_compare %>% 
  filter(kf_tag %in% c("ramp", "card_advantage", "targeted_disruption", "mass_disruption"))
```

## Mechanic Tagging

Overall tagging accuracy is `r mean(is.na(df_compare$kf_tier) == is.na(df_compare$claude_tier))`.  Accuracy for the veggies categories is `r mean(is.na(df_compare_veggies$kf_tier) == is.na(df_compare_veggies$claude_tier))`.

```{r}
df_compare %>% 
  group_by(mechanic = kf_tag) %>% 
  summarise(
    n = n(), 
    accuracy = mean(is.na(kf_tier) == is.na(claude_tier)), 
    .groups = "drop"
  ) %>% 
  arrange(desc(n)) %>% 
  kable()
```


## Tier Tagging

Overall tagging accuracy is `r mean(df_compare$kf_tier == df_compare$claude_tier, na.rm = T)`.  Accuracy for the veggies categories is `r mean(df_compare_veggies$kf_tier == df_compare_veggies$claude_tier, na.rm = T)`.

```{r}
df_compare %>% 
  filter(!is.na(kf_tier), !is.na(claude_tier)) %>% 
  group_by(mechanic = kf_tag) %>% 
  summarise(
    n = n(), 
    accuracy = mean(kf_tier == claude_tier), 
    .groups = "drop"
  ) %>% 
  arrange(desc(n)) %>% 
  kable()
```
